\sysfull

### 2017-11-17 paper/intro.tex
intro: enlarge figure
intro

\begin{figure}
	\includegraphics[width=0.85\columnwidth]{figures/coalescing-is}
    \caption{\label{fig:coalesce}\textbf{An execution of three
statically-defined tasks without (top) and with (bottom) dynamic
coalescing.} Task coalescing at runtime reduces time and energy overhead in
task-based intermittent programming models by performing fewer commits and
buffering updates to non-volatile (NV) variables in volatile (V) memory.}
\end{figure}

@@

Unfortunately, naively merging two atomic tasks might produce a non-atomic task, that may leave memory inconsistent after a partial execution. A merge breaks atomicity when the accesses to non-volatile memory from the previously atomic merged tasks form a \emph{write-after-read (WAR)} dependency.
%
%variables in non-volatile memory at \emph{run-time} that can
%break the atomicity of the \emph{virtual task}. Consider the
%example depicted in Fig.~\ref{fig:virtualization}: Tasks 1,
%2 and 3 being executed consecutively. All tasks in this
%example are atomic since they do not have WAR dependency on
%the persistent variables they are accessing, e.g. \emph{x}
%is only read and \emph{y} is only written within Task 1.
%Now, suppose three tasks have been virtualized into a single
%one at run-time, namely Task 4: since \emph{x} is now first
%\emph{read} and then \emph{written}, a WAR dependency on
%\emph{x} is introduced dynamically at
%run-time---unfortunately Task 4 is \emph{no more atomic}
%since its re-execution will not always produce the same
%results.
%
Although WAR dependencies introduced by the \emph{static} task division can be eliminated at compile time~\cite{alpaca}, those introduced \emph{dynamically} at
run-time cannot. To maintain memory consistency in merged tasks, we propose a
mechanism for \emph{memory virtualization} that buffers the updates to non-volatile variables in volatile memory before committing them at the dynamic task boundary.
%
%Therefore, we require a \emph{new execution
%model} that keeps each virtual task atomic by committing the
%modified persistent variables at the boundary defined
%dynamically at run-time---keeping the non-volatile memory
%unmodified upon a power-interrupt and preserving its
%consistency.

@@

% <<<<<<< HEAD
% We develop \sys%
% \footnote{To be released at \url{http://anonymized.link}}
% %
% : a task coallescing system for task-based
% programming models on intermittently-powered devices. The
% capabilities required for effective coallescing mark our
% contributions:
% >>>>>>> 96e5d9f9b4e97ce8700c375bd8e11708870f5aba
% =======
\textbf{Contributions.} We develop \sys\footnote{To be released at \url{http://anonymized.link}}: a task coalescing system for task-based programming models on intermittently-powered devices. The capabilities required for effective coalescing mark our contributions:
% >>>>>>> 84d7711b6c6f6424cdad97efc8aad96e52f316ff

>>>>

\begin{figure}
	\includegraphics[width=0.95\columnwidth]{figures/coalescing-is}
    \caption{\label{fig:coalesce}\textbf{An execution of three
statically-defined tasks without (top) and with (bottom) dynamic
coalescing.} Task coalescing at runtime reduces time and energy overhead in
task-based intermittent programming models by performing fewer commits and
buffering updates to non-volatile (NV) variables in volatile (V) memory.}
\end{figure}

@@

Unfortunately, naively merging two atomic tasks might produce a non-atomic task, that may leave non-volatile memory inconsistent after a partial execution. A merge breaks atomicity when atomic merged tasks form a \emph{write-after-read (WAR)} dependency---for instance if two tasks \texttt{\{x++\}; \{vector[x]=v;\}} are merged and if the power failure occurs after \texttt{x++}, the value \texttt{x} will be increased twice when the merged task is restarted, that leads to an inconsistency.
%
%variables in non-volatile memory at \emph{run-time} that can
%break the atomicity of the \emph{virtual task}. Consider the
%example depicted in Fig.~\ref{fig:virtualization}: Tasks 1,
%2 and 3 being executed consecutively. All tasks in this
%example are atomic since they do not have WAR dependency on
%the persistent variables they are accessing, e.g. \emph{x}
%is only read and \emph{y} is only written within Task 1.
%Now, suppose three tasks have been virtualized into a single
%one at run-time, namely Task 4: since \emph{x} is now first
%\emph{read} and then \emph{written}, a WAR dependency on
%\emph{x} is introduced dynamically at
%run-time---unfortunately Task 4 is \emph{no more atomic}
%since its re-execution will not always produce the same
%results.
%
Although WAR dependencies introduced by the \emph{static} task division can be eliminated at compile time~\cite{alpaca}, those introduced \emph{dynamically} at
run-time cannot. To maintain memory consistency in merged tasks, we propose a
mechanism for \emph{memory virtualization} that buffers the updates to non-volatile variables in volatile memory before committing them at the dynamic task boundary.
%
%Therefore, we require a \emph{new execution
%model} that keeps each virtual task atomic by committing the
%modified persistent variables at the boundary defined
%dynamically at run-time---keeping the non-volatile memory
%unmodified upon a power-interrupt and preserving its
%consistency.

@@

% <<<<<<< HEAD
% We develop \sys%
% \footnote{To be released at \url{http://anonymized.link}}
% %
% : a task coallescing system for task-based
% programming models on intermittently-powered devices. The
% capabilities required for effective coallescing mark our
% contributions:
% >>>>>>> 96e5d9f9b4e97ce8700c375bd8e11708870f5aba
% =======
\textbf{Contributions.} We develop \sys\footnote{To be released at \url{http://anonymized.link}}: the first task coalescing system for task-based programming models on intermittently-powered devices. The capabilities required for effective coalescing mark our contributions:
% >>>>>>> 84d7711b6c6f6424cdad97efc8aad96e52f316ff
